%corrected

\subsection{Constraints}

For this BSP, we set the different constraints for the ANNs, for the Speech
recognition for the Luxembourgish vocal dataset and the classification model's
implementation.\\

\textbf{Data set.} First, we focus on training our model on a dataset
containing English spoken numbers.~\cite{DBLP:journals/corr/abs-1804-03209}
After having trained the model successfully on this dataset, we train it on the
smaller Luxembourgish dataset and analyse its prediction accuracy. Since we
aren't able to collect as much voice recordings as the English data set, we
should not expect high accuracy.\\

%reference paper

\textbf{Speech recognition.} Since no datasets with continuous sentences of the
Luxembourgish Language exists, we choose to work with isolated word recognition
instead of continuous speech recognition. In isolated word recognition, words are
separated by pauses.\\

\textbf{Speaker dependent.} To simplify the collection of the Luxembourgish
dataset, we collect the audio recordings from one person which makes the
isolated word recognition speaker-dependent.\\

\textbf{Classification problem.} For the presentation of the three required
Neural Network architecture, we set the constraint to present only the Neural
Networks in a classification setting rather than for a regression problem. \\

\textbf{ANNs implementation.} We do not implement the Artificial Neural Networks
architecture since existing deep learning libraries such as Keras are already
matured. Thereby, we focus on explaining how the APIs work and how to use them
in our model.
