\section{Pre-requisites ($[5\%..10\%]$ of total words)} 
\textcolor{gray}{Describe in these sections the main scientific and technical
  knowledge that is required to be known by you before starting the project.  Do
  not describe in details this knowledge but only abstractly. All the content of
  this section shall not used, even partly, in the deliverable sections.}\\

In order to start on the project, certain skills in programming
and mathematics are required. In particular, the preliminary requirement of
the project is as follow:
\begin{itemize}
        \item Understanding of vector and matrix algebra.
        \item Introductory course in Python.
        \item Software development.
        \item Knowledge of probability and statistics, but it is not
                mandatory.
\end{itemize}

\subsection{Scientific pre-requisites}

\textbf{Linear Algebra.}
% \textbf{Linear Algebra.} is a sub-field of mathematics, which works with vectors
% and matrices. Since the input of ML is data that are transformed into structures of
% rows and columns, linear algebra is one of the key foundations of ML. It is used
% to describe the operations of the algorithms, and implement the algorithms in
% code. All tasks in ML relate to linear algebra, from data preprocessing to
% calculating distances in k-NN and vector multiplication in SVM.\\

\subsection{Technical pre-requisites}

\textbf{Python.} Python is an interpreted, high-level and general-purpose
programming language, which is conceived in the late 1980s and released in 1991
by Guido van Rossum.~\cite{PyRo} Its design philosophy accentuates readability
of the code.  As many high-level programming languages, Python is dynamically
typed. Further, it supports multiple programming paradigms such as procedural,
object-oriented and functional programming. I pursued many classes based on
Python whether in high school or at university. During programming fundamentals
1 during semester 1, many Python features were studied such as list
comprehensions, object-oriented programming, etc. I have  a proficient
background in programming in Python to work on this project.\\

\textbf{Software development.} Software development is the process of designing
and implementation of applications and frameworks. In general, the process of
software development is writing and maintaining the source code which is often a
planned and structured process. The software development contains mostly
research, prototyping, modification and reuse of existing software. During the
technical deliverable section, we use this structured process to design and
implement our ANNs. 
