% correcte VD

\section{Project description}
\subsection{Domains}

\begin{itemize}
        \item Speech Recognition
        \item Artificial Neural Networks
        \item Deep Learning 
        \item Data preprocessing
        \item Training set and testing set
        \item Python
        \item Keras
\end{itemize}

\subsubsection{Scientific}

The scientific aspects covered by this Bachelor Semester Project are the
concepts of speech recognition and Deep Learning. Different Artificial Neural
Networks (ANN) architectures are investigated for the end-to-end isolated word
recognition task.\\

\textbf{Speech Recognition.} The objective of speech recognition is to map an
audio signal which contains a set of spoken natural language expressions to the
matching sequence of words produced by the speaker. In the past, Automatic
Speech Recognition (ASR) was made up of different modules such as complex
feature extraction, acoustic models, language and pronunciation
models.~\cite{DBLP:journals/corr/AmodeiABCCCCCCD15} Sequential models, such as
Hidden Markov Models (HMM), in combination with a pre-trained language model,
were used to map sequences of phones to output words.~\cite{Williamsong} A
different approach is to build ASR models end-to-end. With deep learning, it
replaces most of the modules with a single module. This alternative method will
be the main task of this report.\\

\textbf{Artificial Neural Networks (ANN).} ANNs are computing systems inspired
by the biological brain. These systems are based on a set of connected units
called artificial nodes. Each connection can transmit \textit{signals} between
units. A unit can process the signal and transmit it to another unit.\\

\textbf{Deep Learning.} This field deals with learning by decomposing a task's
input into smaller and simpler compositions. With Deep Learning, computing
systems can build complex concepts from a composition of simpler concepts.

\subsubsection{Technical} The technological aspect which is covered in this
project is the data collection, feature extraction and implementation of the
end-to-end spoken word recognition model. \\

\textbf{Data preprocessing.} Data preprocessing is an important phase in machine
learning. It ensures the quality of the gathered data by eliminating irrelevant
and redundant information. Data preprocessing contains tasks such as cleaning,
instance selection, normalization, feature extraction and selection. We will
focus on feature extraction in this paper with the presentation of Mel-frequency
cepstral coefficients (MFCCs) in Section~\ref{mfccs} which are used as features
extracted from the speech signal.\\

%add section

\textbf{Training set and testing set.} For a computing system to learn from and
make predictions on data, a mathematical model is built from input data. This
input data used to create the model consists of two datasets: The training and
testing set. The training set contains pairs of an input vector, which represent
features and an output vector often called the labels. With the training set,
the model learns to map the input vector to the labels. On the other hand, the
testing set evaluates how well the model generalizes the prediction over the
dataset previously not seen by the model.\\

\textbf{Python.} This is a programming language which is interpreted, high-level
and general-purpose.~\cite{Python}\\

\textbf{Keras Library.} \textit{Keras} is a high-level Neural Networks API
written in Python. It is designed for easy-to-use and efficient experimentation
with Deep Learning.~\cite{chollet2015keras}
