% corrected

% introduction

Before we can train our ASR model, we have to process our audio data. The first
task is to extract features from the data which describes natural languages
expressions and excludes background noises and emotions.\\

% def of MFCCs

Mel Frequency Cepstral Coefficients (MFCCs) are a feature generally used in ASR.
MFCCs were presented by Davis and Mermelstein in the 1980s.~\cite{mfcc}\\

To extract the MFCCS from the dataset, the following extraction steps have to be
executed on a speech signal sampled at $16kHz$:\\

\begin{enumerate}[label=\arabic*.]
  \item Frame the signal into short frames.\\
  
  Frame the signal into $25ms$ frames. The frame length of a $16kHz$ signal:
  \begin{center} 
    0.025*16000 = 400 samples.
  \end{center}
  With a frame step of $160\ samples$ or $10ms$, the frames overlap themselves.
  Such that the first $400\ samples$ frame start at sample 0 and the second
  frame starts at sample 160. This pattern repeats until the end of speech
  signal. If the audio file is not divisible by an even number, it is padded by
  zeros until it is.\\
  \item For each frame calculate the periodogram estimate of the power spectrum.
    To obtain the Discrete Fourier Transform (DTF) from the frame $i$, we
    perform:
    \begin{center}
      \[S_{i}(k) = \sum_{N}^{n=1}s_i(n)h(n)e^{-j2\pi kn/N}\]
    \end{center}
    For each speech frame $s_{i}(n)$, the periodogram-based power spectral
    estimate is calculated with:
    \begin{center}
      \[P_{i}(k)=\frac{1}{N}{\mid{S_{i}(k)}\mid}^{2}\]
    \end{center}
  This is called the Periodogram estimate of the power spectrum which identifies
  for every frame which frequencies are present. The first 257 coefficients are
  kept from the 512 points fast Fourier transform which is an algorithm to
  compute the DTF.\\
  \item Apply the Mel filterbank to the power spectral and sum the energy in
    each filter. The Mel filterbank is a set of 26 triangular filters. The
    filterbank energies are calculated by multiplying every filterbank with the
    power spectrum and adding the coefficients kept in the previous step.\\
  \item Take the logarithm of the 26 filterbank energies.\\
  \item Take the Discrete Cosine Transform (DCT) of the 26 log filterbank
    energies resulting in 26 cepstral coefficients. We only used the lower 12-13
    of the 26 coefficients for ASR.\\
\end{enumerate}

\textcolor{gray}{figures to be added}
